\vskip-0.6in \Large Political Uncertainty

### 2015-06-02 GS-extension.tex
start conditions for two positive bribes

The full set of FOCs (in logistic form) is then:
\[
    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
\]
\[
    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
\]
\[
    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
\]
\[
  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(-\frac{1}{2}\right) = 0 
\]
There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = \left(b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\

@@

>>>>

The full set of FOCs (in logistic form) is then:
\[
    W_B\frac{e^{-X}}{\left(1+e^{-X}\right)^2}\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_X = 0
\]
\[
    W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \right] - 1 + \lambda_Y = 0 
\]
\[
    W_B\frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}\left[\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \right] - 1 + \lambda_Z = 0
\]
\[
  b\left(0\right) \geq0 \hskip.2in b\left(\frac{1}{2}\right) \geq0 \hskip.2in b\left(-\frac{1}{2}\right) \geq0 
\]
\[
  \lambda_X \geq0 \hskip.2in \lambda_Y \geq0 \hskip.2in \lambda_Z \geq0 
\]
\[
  \lambda_X \cdot b\left(0\right) = 0 \hskip.2in \lambda_Y \cdot b\left(\frac{1}{2}\right) = 0 \hskip.2in \lambda_Z \cdot b\left(-\frac{1}{2}\right) = 0 
\]
There are 8 patterns of positive and zero components in the 3-dimensional vector of bribes, $b' = (b\left(0\right),b\left(\frac{1}{2}\right), b\left(-\frac{1}{2}\right)\right)$. \\

@@

\vskip.5in
Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
\begin{itemize}
	\item Then $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = -\frac{\beta}{2} - \alpha $
	\item $\lambda_Z$ is likely positive
	\item $\lambda_X = \lambda_Y = 0$
\end{itemize}
So we'll have $-Z = -X-Y$
\begin{itemize}
	\item Which is
		\[
		  \frac{\beta}{2} + \alpha = \alpha - b(0) - \frac{\beta}{2} + \alpha - b\left(\frac{1}{2}\right)
		\]
		\[
		  \beta = \alpha - \left(b(0) + b\left(\frac{1}{2}\right) \right)
		\]
\end{itemize}
